### 2020-04-29 README.Rmd
Update results for Bristol

```{r}
bristol_centre = tmaptools::geocode_OSM("Bristol", as.sf = TRUE)
bristol_buff = stplanr::geo_buffer(bristol_centre, dist = 1500)
roads_top = roads[bristol_buff, ] %>%
  filter(length > 200) %>% 
  arrange(desc(pctgov)) %>%
  slice(2:10) %>% 
  distinct(name, .keep_all = TRUE)
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_scale_bar()

>>>>

```{r}
bristol_centre = tmaptools::geocode_OSM("Bristol", as.sf = TRUE)
bristol_buff = stplanr::geo_buffer(bristol_centre, dist = 1500)
roads_top = roads[bristol_buff, ] %>%
  filter(length > 300) %>% 
  filter(!name == "Bond Street", !name == "") %>% 
  arrange(desc(pctgov)) %>%
  slice(2:11) %>% 
  distinct(name, .keep_all = TRUE)
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_scale_bar()
